---
title: "2021_03_15_Video_Games"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
library(lubridate)
library(jsonlite)
options(scipen = 999)
```

## Video Games (TidyTuesday 2021_03_15)

### Data Dictionary (games.csv)

| variable        | class           | description  |
| ------------- |:-------------:| -----:|
gamename |	character |	Name of video games
year |	double	 | Year of measureo
month |	character |	Month of measure
avg	 | double |	Average number of players at the same time
gain |	double |	Gain (or loss) Difference in average compared to the previous month (NA = 1st month)
peak |	double |	Highest number of players at the same time
avg_peak_perc |	character	 |Share of the average in the maximum value (avg / peak) in %


### Read-in the Data
```{r}
# Or read in the data manually
games <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-16/games.csv', 
                        col_types = cols(year=col_character(), 
                                         avg_peak_perc=col_number()))
spec(games)
problems(games)
games[41807,]
```

## Understand the Data

What are the top 10 games by avg player count in the dataset?
```{r}
games %>% group_by(gamename) %>% filter(avg == max(avg)) %>% arrange(desc(avg)) %>% ungroup() %>% slice(1:25)
```

# Question of Interest
Can we predict initial player counts for new games?

Some Assumptions:
- Games might release at any point in a month.
- Assumption: Let's use the max values for the first 3 months to account for any low initial counts due to releasing at the end of a month, etc.


# Fun with dates!
```{r}
# Add a date column using lubridate
games <- games %>% mutate(date = mdy(str_c(month,"-01-",year)))
games

# Make some assumptions...
# Cut off 2012 games and 2021 games as those may not be complete
games <- games %>% filter(!(year %in% c('2012','2021')))
games

# Find Initial Releases
initial_release <- games %>% filter(is.na(gain) == T)  %>% select(gamename, date) %>% mutate(date_end = date + months(3))
initial_release

# Join Initial Releases back to games where gamename == gamename and initial_release$date is >= date and date + 3 months
install.packages('sqldf')
library(sqldf)

initial_release_3m_df <- sqldf("SELECT * FROM initial_release
            LEFT JOIN games
            ON  initial_release.gamename  = games.gamename
            AND games.date BETWEEN initial_release.date AND initial_release.date_end")
initial_release_3m_df

# Remove some dup columns
initial_release_3m_df <- initial_release_3m_df %>% select(1:3, 5:9)
initial_release_3m_df

# Ensure we only have one row per game
initial_release_3m_df <- initial_release_3m_df %>% group_by(gamename) %>% summarise(max_3m_avg = max(avg), max_3m_peak = max(peak), release_year = min(year), release_month = min(month) ) 

initial_release_3m_df %>% arrange(desc(max_3m_avg))
```

# Histogram of all initial releases from 2013 to 2021 with at least 1 player
games %>% filter(is.na(gain) == T, avg >= 1)  %>% ggplot(aes(x=avg)) + geom_histogram(binwidth=1000)
initial_release_3m_df %>% ggplot(aes(x=max_3m_avg)) + geom_histogram(binwidth=100)
initial_release_3m_df %>% filter(max_3m_avg >= 100, max_3m_avg < 1000) %>% ggplot(aes(x=max_3m_avg)) + geom_histogram(binwidth=100)

# Distribution
games %>% filter(is.na(gain) == T, avg >= 1)  %>% ggplot(aes(x=factor(month, month.name), y=avg)) + geom_boxplot()
```

## Augment the Data with the IGDB Rest API

Capture Data from igdb Rest API
https://www.igdb.com/advanced_search

## Get Access Token from Twitch so we can use the IGDB API
```{r}

twitch_client_id = 'x3vdptwoaut0p9kq5k2x0my7n2v2j3'
twitch_secret_key = 'orlgkwfb2ybdus0984wyawx6jnx95i'

# Get API Access token

# POST(
#   url = NULL,
#   config = list(),
#   ...,
#   body = NULL,
#   encode = c("multipart", "form", "json", "raw"),
#   handle = NULL
# )

# Make a post request to get oauth access token
url = str_c("https://id.twitch.tv/oauth2/token?client_id=", twitch_client_id, "&client_secret=", twitch_secret_key,"&grant_type=client_credentials", sep="")
r = POST(url = url)
# What we got back
str(content(r))

# What we need
access_token = content(r)$access_token
```

## Example IGDB API to get all the fields of metadata about a game
All calls to the IGDB are posts.  
- The URL is the endpoint, we will work mainly with *games*.
- The header needs the Client-ID from twitch and our Access Token.
- The body is raw text and contains their propritary sql like query language.

https://api-docs.igdb.com/#examples

```{r}
url = "https://api.igdb.com/v4/games"

# Client-ID: abcdefg12345
# Authorization: Bearer prau3ol6mg5glgek8m89ec2s9q5i3i
# fields *;

body = 'fields *;'

# add headers needs a named character vector
bearer_token = str_c("Bearer ", access_token, sep="")
header_named_vector = c("Client-ID" = twitch_client_id, "Authorization" = bearer_token)
header_named_vector

r_games = POST(url, add_headers(header_named_vector), body = body, encode = "raw")

str(content(r_games))
```

Create a function to get the meta data for a single game
```{r}

lookup_game_metadata <- function(game_name, access_token) {
  url = "https://api.igdb.com/v4/games"
  header = c("Client-ID" = twitch_client_id, "Authorization" = bearer_token)
  body = str_c("fields name,rating,rating_count,follows; where name = \"", game_name, "\";", sep ="")
  
  Sys.sleep(0.26) #sleep .26 second so we do not get rate limited (max is 4 requests per second)
  return(content(POST(url, add_headers(header_named_vector), body = body, encode = "raw")))
}
```

# Test it
```{r}
lookup_game_metadata("Rust", access_token)
```

# Get the data for 10 random games
```{r}
sample_games <- games %>% sample_n(10)
sample_games
l <- sapply(sample_games$gamename, lookup_game_metadata, access_token=access_token)


df <- data.frame(matrix(ncol = 5, nrow = 0))
for(e in l) {
  for(g in e) {
   df <- rbind(df, c(g$id, g$name, g$rating, g$rating_count, g$follows)) 
  }
}

colnames(df) <- c("id", "name", "rating", "rating_count", "follows")
df <- as_tibble(df)
df
```

# Combine our Dataframes

# H2o.ai
Install H2o.ai for R  
```{r}
# The following two commands remove any previously installed H2O packages for R.
if ("package:h2o" %in% search()) { detach("package:h2o", unload=TRUE) }
if ("h2o" %in% rownames(installed.packages())) { remove.packages("h2o") }

# Next, we download packages that H2O depends on.
pkgs <- c("RCurl","jsonlite")
for (pkg in pkgs) {
  if (! (pkg %in% rownames(installed.packages()))) { install.packages(pkg) }
}

# Now we download, install and initialize the H2O package for R.
install.packages("h2o", type="source", repos="http://h2o-release.s3.amazonaws.com/h2o/rel-zermelo/4/R")

# Finally, let's load H2O and start up an H2O cluster
library(h2o)
h2o.init()

```

## Use H2o.ai
```{r}

```



